Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375

### 2015-04-22 papers/B1555_EdgeOn/B1555_letter.tex
Rewrite Discussion for new comments

% Journal definitions
\newcommand{\apj}[1]{ApJ}
\newcommand{\mnras}[1]{MNRAS}
\newcommand{\apjl}[1]{ApJL}
\newcommand{\pasj}[1]{PASJ}
\newcommand{\aj}[1]{AJ}
\newcommand{\nat}[1]{Nature}

@@

A common feature of simulations of structure formation is the presence
of thousands of subhaloes that are associated with larger mass haloes.
However, observations of the Local Group find many fewer satellite
galaxies than are predicted by the simulations, even when taking into
account completeness corrections arising from the limited sky coverage
imposed by the Galactic Plane.  This is the famous ``missing
satellite'' problem \citep{Klypin1999, Moore1999, S07}. In order to
understand this discrepancy, it is imperative to build up a large
sample of satellites/subhaloes in galaxies outside the Local Group.
This process is challenging due to the faintness of the satellite
galaxies.  Furthermore, lower-mass satellites may not be able to
retain the gas needed for ongoing star formation \citep[e.g.,][]{P11},
rendering them effectively dark.  These factors make gravitational
lensing a powerful and promising tool for the detection of
substructure.

It was first suggested by \citet{Mao1998} that flux ratio anomalies observed in radio loud multiple images of lensed quasar could be interpreted as the telltale of the presence of substructure in lens galaxies.
%Flux ratio anomalies are seen in strong lensing systems which have multiple images that are spacially close to each other. These ``merging doubles'' share the same surface brightness in principle but happend to have different surface brightness. 
Indeed, small perturbations in the gravitational potential are
sufficient to bring flux ratio anomalies in strong lensed systems.
Moreover, unlike in the optical or infrared, in the radio band, lensed
images are not sensitive to micro lensing from stars nor dust
extinction.  This makes flux ratio anomalies a promising tool to
detect dark matter substructures \citep{Dalal2002, N13}.  At present,
the amount of substructure derived from flux ratio anomalies is in
disagreement with predictions from numerical simulations, with the
former requiring a larger fraction of mass in substructure than
expected \citet{Xu14}. While this could be the result of small sample
statistics, it could also be the indication that flux ratio anomalies
have a different origin than substructure. 
%
An alternative method for
the detection of substructure in gravitational lens galaxies based on
the surface brightness distribution of extended arcs and Einstein ring
has been introduced by \citet{K05,V09}. Interestingly, the fraction of
substructure measured with this \emph{gravitational imaging technique}
is currently in agreement with theoretical expectations \citep{V14a}.

@@

As a first trail of modelling, we create a single SIE model to 
justify the perforamnce of a simple lensing potential. Like previous studies
\citep{Marlow, Xu14}, flux anomaly in B1555+375 cannot be predcited
with a single elliptical lensing potential. 
We then create two separate models of the lensing potential.  In the
first we treat the lens as a SIE bulge and an exponential edge-on disk
(SIE+expdisk).  In the second model the disk is represented as a very
elongated SIE component (2-SIE).  The lens system is red, with a
strong jump in flux between the F814W (roughly I) and F160W (roughly
H) bands (Fig.~\ref{fig:multiband}), so we assign a lens redshift of
$z_\ell = 1.0$ and a source redshift of $z_s =1.5$.  The full best-fit parameters are shown in Table
2. Both of these models predict fairly matched results with the radio
observation, and the 2-SIE model has a better performance in flux
ratios. The comparison of observation and our lens modelling is given
in Figure 3 and Tables 3 \& 4.

@@

Gravitational lensing is [one of] the most powerful methods for
studying substructure in galaxies outside of the Local Universe, and
the flux ratio anomaly systems are a key aspect of these
investigations.  However, before using the flux ratio anomaly in any
given system to investigate structure formation and the properties of
dark matter, it is critical to eliminate other possible explanations
for the difference between the observed and expected fluxes.  It
is for this reason that much of the effort in the flux-ratio technique
has been focused on radio-loud lens systems.  At these wavelengths,
dust extinction and microlensing effects should be minimal (although
see \citet{K2000} for a rare example of radio microlensing).
Radio propagation effects can  affect radio fluxes, as is clearly
shown in the B0128 system [REF??, In Dandan's paper?].  However, these propagation effects
can be disentangled from substructure lensing because they have well
known dependencies on wavelength. [COMMENTS ABOUT B1555 AND OTHER
RADIO-LOUD SYSTEMS, from K03 paper].

In our models based on the new imaging from the SHARP $K^{\prime}$
band observations, the most significant difference in comparison to
previous modelling is a new edge-on disk component. With a bulge plus
an edge-on disk, our models produce matches to both the radio image
positions and flux ratio anomalies, while models with only one SIE
component \citep{Marlow,Xu14} fail to reproduce the fluxes
correctly. Our successful modelling indicates that the
kiloparsec-scale structure of lens galaxy itself is sufficient to
explain the flux ratio anomalies in B1555+375, without any need to
invoke the presense of substructrue. This breaks the idea that in
strongly lensed quasars, radio flux ratio anomalies are most likely
originated from substructure perturbations. It is worth noticing not
all of flux ratio anomalies in lensed quasars indicate the existence
of substructures. Our discovery shows a complex lens galaxy mass
distribution can dominate flux ratio anomalous phenomena in a strongly
lensed system.

Recent studies on numerical simulation support our discover on B1555+375. In \citet{Xu14}, they found that substructures cannot expalin all radio flux anomalous phenomena in radio loud lensed systems. By adding subhaloes on to those systems, only one out of six lens systems reproduces the flux anomalies. The rest of them are unlikely (only few percent likelihood) to have substructure originated flux anomalies, including our target B1555+375. \citet{Xu14} conclude the failure in predicting fluxes of those lens systems is due to improper lens models. Their results are consistent with the SHARP $K^{\prime}$ band observations, which in B1555+375, an edge-on disk lies cross the radio merging double. Here we would like to draw attention to the possible impacts on substructure searching from the enge-on disk orginated flux anomalies. In SHARP observations, we find B1555+375 is not the only system having edge-on disk detection in high resolution near-infrared imaging (see Fig 4). It is a sign that researchers should be careful about the flux anomalies fraction in lensed quasars. It may be worth considering an upper limit of flux anomalies fraciton from observation results to avoid over estimate the number of substructure detections. Although the number of radio loud flux anomalous lensed quasars remains small, a new technique using narrow-line emissions will enlarge the sample and bring statistical perspective on substructures in the near future \citep{N14}. For further analysis on substurcture population, mass function etc., it is always important to rule out other non-substructure effects.

>>>>

% Journal definitions
\newcommand{\apj}[1]{ApJ}
\newcommand{\mnras}[1]{MNRAS}
\newcommand{\apjl}[1]{ApJL}
\newcommand{\pasj}[1]{PASJ}
\newcommand{\aj}[1]{AJ}
\newcommand{\nat}[1]{Nature}
\newcommand{\aap}{A\&A}

@@

A common feature of simulations of structure formation is the presence
of thousands of subhaloes that are associated with larger mass haloes.
However, observations of the Local Group find many fewer satellite
galaxies than are predicted by the simulations, even when taking into
account completeness corrections arising from the limited sky coverage
imposed by the Galactic Plane. [NEED REF]  This is the famous ``missing
satellite'' problem \citep{Klypin1999, Moore1999, S07}. In order to
understand this discrepancy, it is imperative to build up a large
sample of satellites/subhaloes in galaxies outside the Local Group.
This process is challenging due to the faintness of the satellite
galaxies.  Furthermore, lower-mass satellites may not be able to
retain the gas needed for ongoing star formation \citep[e.g.,][]{P11},
rendering them effectively dark.  These factors make gravitational
lensing a powerful and promising tool for the detection of
substructure.

It was first suggested by \citet{Mao1998} that flux ratio anomalies observed in radio loud multiple images of lensed quasar could be interpreted as the telltale of the presence of substructure in lens galaxies.
%Flux ratio anomalies are seen in strong lensing systems which have multiple images that are spacially close to each other. These ``merging doubles'' share the same surface brightness in principle but happend to have different surface brightness. 
Indeed, small perturbations in the gravitational potential are
sufficient to bring flux ratio anomalies in strong lensed systems \citep{Bradac02}. 
Moreover, unlike in the optical or infrared, in the radio band, lensed
images are not sensitive to micro lensing from stars nor dust
extinction.  This makes flux ratio anomalies a promising tool to
detect dark matter substructures \citep{Dalal2002, N13}.  At present,
the amount of substructure derived from flux ratio anomalies is in
disagreement with predictions from numerical simulations, with the
former requiring a larger fraction of mass in substructure than
expected \citet{Xu14}. While this could be the result of small sample
statistics, it could also be the indication that flux ratio anomalies
have a different origin than substructure. 
%
An alternative method for
the detection of substructure in gravitational lens galaxies based on
the surface brightness distribution of extended arcs and Einstein ring
has been introduced by \citet{K05} and \citet{V09}. Interestingly, the fraction of
substructure measured with this \emph{gravitational imaging technique}
is currently in agreement with theoretical expectations \citep{V14a}.

@@

As a first trail of modelling, we create a single SIE model to 
justify the perforamnce of a simple lensing potential. Like previous studies
\citep{Marlow, Xu14}, flux anomaly in B1555+375 cannot be predcited
with a single elliptical lensing potential. 
We then create two separate models of the lensing potential.  In the
first we treat the lens as a SIE bulge and an exponential edge-on disk
(SIE+expdisk).  In the second model the disk is represented as a very
elongated SIE component (2-SIE).  The lens system is red, with a
strong jump in flux between the F814W (roughly I) and F160W (roughly
H) bands (Fig.~\ref{fig:multiband}), so we assign a lens redshift of
$z_\ell = 1.0$ and a source redshift of $z_s =1.5$.  The full best-fit parameters are shown in Table
2. Both of these models predict fairly matched results with the radio
observation, and the 2-SIE model has a better performance in flux
ratios. The comparison of observation and our lens modelling is given
in Figure 3 and Tables 3 \& 4.
[WHY NO EXTERNAL SHEAR?---WE THINK WITH ONLY RADIO DATA ITS LACK OF CONSTRAINT]

[WHERE DO WE PUT MODEL CHI-SQUARE??]

@@

Gravitational lensing is [one of] the most powerful methods for
studying substructure in galaxies outside of the Local Universe, and
the flux ratio anomaly systems are a key aspect of these
investigations.  However, before using the flux ratio anomaly in any
given system to investigate structure formation and the properties of
dark matter, it is critical to eliminate other possible explanations
for the difference between the observed and expected fluxes.  It
is for this reason that much of the effort in the flux-ratio technique
has been focused on radio-loud lens systems.  At these wavelengths,
dust extinction and microlensing effects should be minimal (although
see \citet{K2000} for a rare example of radio microlensing).
Radio propagation effects can  affect radio fluxes, as is clearly
shown in the B0128 system \citep{B04}.  However, these propagation effects
can be disentangled from substructure lensing because they have well
known dependencies on wavelength. \citet{KD04} examine all eight radio loud flux anomalous lenses: MG 0414+0534, B0712+472,  B1359+154, B1422+231, B1555+375, B1608+656, B1933+503, and B2045+265. 
They find no strong wavelength dependence in the flux ratios of all these systems and rule out the possible affects from radio propagation.

In our models based on the new imaging from the SHARP $K^{\prime}$
band observations, the most significant difference in comparison to
previous modelling is a new edge-on disk component. With a bulge plus
an edge-on disk, our models produce matches to both the radio image
positions and the flux ratio, while models with only one SIE
component \citep{Marlow,Xu14} fail to reproduce the fluxes
correctly. Our successful modelling indicates that the
kiloparsec-scale structure of lens galaxy itself is sufficient to
explain the flux ratio anomalies in B1555+375, without any need to
invoke the presense of substructrue. This breaks the idea that in
strongly lensed quasars, radio flux ratio anomalies are most likely
originated from substructure perturbations. Our discovery shows a complex lens galaxy mass
distribution can dominate flux ratio anomalous phenomena in a strongly
lensed system.

From theoretical perspective, \citet{Xu14}  find that substructures cannot expalin radio flux anomalies in all these lenses. By adding subhaloes from numerical simulations on to these systems, only one out of eight radio loud systems reproduces the flux anomalies. The rest of them are unlikely (only $1 \% - 4 \%$ probability) to have substructure originated flux anomalies, including our target B1555+375. Among those eight radio lenses, B1555+375 is one of the most anomalous systems, but it is also one of the most challenging systems to explain by substructures. \citet{Xu14} conclude the failure in predicting flux ratios is due to oversimplified/improper lens modelling. They also outline that the SIE component and the external shear are orthogonal indicates a possible missing ingredient in lens model. Their results are consistent with the SHARP $K^{\prime}$ band observations, which an edge-on disk lies cross the radio merging double in B1555+375. B1555+375 is not the only system having edge-on disk detection in SHARP near-infrared AO imaging (see Fig 4). We would like to draw attention to the possible impacts on substructure searching from this enge-on disk orginated flux anomalies. It is a sign that researchers should be careful about the flux anomalies fraction in lensed quasars. It may be worth considering an upper limit of flux anomalies fraciton from observation results to avoid over estimate the number of substructure detections. Although the number of radio loud flux anomalous lensed quasars remains small, a new technique using narrow-line emissions will enlarge the sample and bring statistical perspective on substructures in the near future \citep{N14}. For further analysis on substurcture population, mass function etc., it is always important to rule out other non-substructure effects.
